Impact of interaction network structure on community-level plant reproduction success

### 2019-02-28 paper_round2.Rmd
new changes in response to Nacho´s comments. Discussion advanced.

Title: Impact of interaction network structure on community-level plant reproduction success  
or "Interaction network structure maximizes community-level plant reproduction success via [niche complmentariety?]()"

@@

Short running title: Network structure effects on function

Keywords: nestedness, functional complementary, fruitset, pollination, plant-pollinator interaction

@@

Words in Abstract: 149 words

@@

Declines in pollinator diversity and abundance have been reported across different regions, with implications for the reproductive success of many plant species. However, research has targeted the consequences for individual plant species, particularly focusing on pairwise plant-pollinator interactions, and largely overlooking community-level dynamics. Yet species do not interact in isolation, they are embedded within larger networks whose structure can affect pollinator functional roles and, ultimately, the pollination services they deliver to plants. Here, we present one of the first efforts linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 well-resolved networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems. We find that, for prediction purposes, information on simple visitation metrics is sufficient. Contrastingly, a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on network structure [such as...]().

@@

Pollinators provide key services to plants by facilitating pollen flow between individuals. The recent declining trends found for some pollinator species in some regions of the planet ([@Potts2010], although see [@Herrera2018] for opposite trends[IB: I think Herrea paper is not needed here, as is quite local. My 2018 Phil Trans paper sumarizs the lack of knowledge for the world]()), have led many researchers to focus on the functional impacts of these changes in pollinator diversity, with a major focus being placed on the consequences for plant reproductive success [@Biesmeijer2006].

Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012a; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain differences found  across different plant individuals. Some have gone a step further by including information on the efficiency of these visits, thus adding a measure of quality to the pollination services (REF[I only know refs for crops, e.g. winfree. Check Morris Ecology 2010 to see if there is something tehere]()). Contrastingly, community-level analyses remain scarce [@Bennett2018]. Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species. We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect ones between species within one guild (e.g., plants) through their shared resources [@Lazaro2014, [Carvalheiro et al 2014 Ecol Lett, and Mayfield ans Stouffer 2017 Nature EcoEvo]()]. Understanding how changes in pollinator diversity [diversity or interaction structure?]() affect whole community assemblages is thus a major challenge that requires attention.

The few pollination studies that have analysed the effects of changing pollinator diversity for reproductive success at the community level, have done so using mainly experimental setups. As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found that not only pollinator species diversity had an effect for average reproductive success, but also they found that the structure that shaped the community had an important effect [@Frund2013]. In particular, these authors found that the functional complementarity between pollinators, in terms of plant species and temperature coverage (a measure of the overlap in the use of plant resources and optimum temperature activity) had a positive effect for average seed set at the community level [@Frund2013]. This provides added information on the effects of biodiversity for ecosystem functioning, suggesting that not only the diversity of species present but also the diversity of roles and ways in which a community is structured are determinant factors.

Indeed, theoretical research has long suggested that the structure of a community has an effect for ecosystem functioning (reviewed in [@Thompson2012]). This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data [(but see Poisot and Gravel Ecol Let?)](). Specifically, a major knowledge gap resides in understading which aspects of structure determine which aspects of function [@Thompson2012]. We are now at a point in which there is considerable understanding on the attributes characterizing mutualistic interaction networks ([Bacompte and H¿JOrdano AREES review]() REF, REF, REF) and we have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016]. Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures ([Bascompte et al 2013 PNAS]()) or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004]. However, how the structure formed by this network of interactions afects key ecosystem functions such as plant reproduction remains untested [(Winfree BAAE opinion paper is good to cite "Global change, biodiversity, and ecosystem services: What can we learn from 6 studies of pollinators?")](). The time is thus ripe to use this knowledge to explore relationships between community structure and ecosystem functioning, with special emphasis being placed on the underlying mechanisms that drive these relationships.

Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level. To this end, we use a well-replicated dataset encompassing 16 well-resolved networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain. Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success. In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success [and equity acorss species.]()

Our results suggest that for prediction purposes, information on simple visitation metrics, particularly regarding the diversity of pollinators that visit a plant species, is sufficient. However, we find that a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success requires additional information on network structure, notably information on the complementarity between the functions performed by different pollinator species.

[IB: this intro is brilliant!]()

@@

Our study was conducted in SW Spain within the area of influence of Doñana National Park (Figure 1?). Here, we surveyed 16 Mediterranean woodland patches, located within a XXX m2 area and with an average distance of XX km between them (min= XX, max= XX). [SHOULD WE SAY SOMETHING ABOUT THE MATRIX SURROUNDING THESE SITES OR THE TYPE OF VEGETATION PRESENT IN THEM??? IB: I don't think is relevant. ASK CURRO ABOUT THE NUMBERS ABOVE.]() Each site was surveyed 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins. Along each transect, we identified all plant species and recorded all the flower visitors [IS IT JUST BEES AND HOVERFLIES? IB: NO, ALL VISITORS!]() that legitimately visited them. Floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FdPM with the aid of experts in the different taxonomic groups (see acknowledgements). All surveys were done under similar weather conditions, avoiding windy or rainy days.

@@

Within each site, we marked between 2 and 12 individuals (6.49 +- 2.37) of 1 [NB: Which site has only one species!]() to 6 plant species (4.06 +- 1.69), depending on the availability and presence of flowers during the sampling events. For each individual, we counted the number of flowers at each sampling point and recorded fruit set, the number of seeds per fruit (for 2-36 fruits, 11.17 +- 6.84) and average seed weight per fruit at the end of the season. Our survey included a total of 19 different plant species across our 16 sites.

@@

In order to analyse how differences within the pollinator community might affect plant reproductive success, we constructed weighted interaction networks by pooling the data for the 7 rounds of sampling. We thus obtained one weighted interaction network per site, representing the frequency of visits by different pollinator species to different plant species. For each network, we then proceeded to extract a series of relevant network metrics.

@@

At the community level, we followed the same logic as the one presented at the species level. Thus, we also calculated two network metrics providing complementary non-redundant information. In this case we focused on (i) nestedness and (ii) functional complementarity. Nestedness is the property by which specialists interact with a subset of the species that generalists interact with ([Bascompte et al 2003 PNAS]). Although there is an ongoing debate in the literature, some studies have found that nested networks are more stable and resilient to perturbations because nestedness implies a certain level of redundancy and thus the possibility for functional replacement in the case of species loss (REF). [We used the widely accepted NODF metric to calculate Nestedness]() However, plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]). Yet at present we do not know how the interplay between redundancy and complementarity in species roles determines reproductive success. [To calculate functional complmentariey we used ...](). All network analysis were perfeormed using bipartite package.

Many network attributes vary with network size and complexity [@Bluthgen2006]. In the case of nestedness, we know it can be affected by network size and connectance (REF). An approach that is often used to correct for this, is to use null models and to compare null-model corrected nestedness values across different networks. However, this approach has been recently shown to present the same issues, as z-scores also change with network size and connectance [@Song2017]. Given the dependence of nestedness on network size and connectance, we followed the advice of these researchers by using a normalized value of nestedness, NODFc, calculated as XXXX, where XXXXX [INCLUDE FORMULA AND DEFINE CONCEPTS], which is independent of network size and thus comparable across different networks [@Song2017]. All network metrics were calculated using package bipartite [@Dormann2009].

@@

At the species level, model 1 included as explanatory variables the diversity of pollinator species visiting a focal plant and the total number of visits received by that plant species; while model 2, added the two network attributes calculated at the species level: average niche overlap and centrality. In this case, we included plant species nested within site as a random effect to account for the non-independence of several individuals measured for the same plant species within each site. The diversity of pollinator species visiting a focal plant was approximated using the plant´s normalised degree, i.e., the number of links with different pollinator species a plant has, scaled by the number of possible partners [@Dormann2009].

At the community level, we upscaled our species-level analyses. In this case, model 1 included total pollinator diversity and the total number of visits received by all plants within the community as explanatory variables. Model 2, in turn, added information on community structure by including nestedness and functional complementarity as explanatory variables. As response variable we had the average reproductive success for the whole community (i.e., average fruitset, average number of seeds per fruit previously scaled for each species, and average fruit and seed weight [IB: also scaled?]()). We thus, had a single value per site and no random effects are needed in this case.

Average values of reproductive success at the community level can be driven to a large extent by a single plant species. Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” in reproductive success across the whole community. We therefore calculated a measure of equity in reproductive success at the community level as the proportion of plant species within a site that is at 50% of the maximum value of fruitset recorded for that plant species within our sampling. We repeated this using 25% and 75% thresholds. We then used the same framework as before and fit the same models 1 and 2 as the ones used at the community level, but using equity in reproductive success as the response variable. [Here is unclear how the proportion is calculated. This is: average fruit set per species is > 50%? Or as we discussed a more coplex option can be: % of species which > 50 % of individuals had seed set > 50%. Now that I see this I would only used if we gain a lot, otherwise is too complicated. Also, I removed species present is only one (or two) sites for this analysis, because the % was forces to be 1. If you kept this in your analysis, should be explained]().

We used information criterion methods to find the best model for each case and selected the ones with the lowest Akaike Information Criterion (AIC) value. Differences in AIC values < 2, were not considered enough to select one model over the other [@Burnham2011].

@@

Finally, we tested whether the importance of community structure in explaining differences in reproductive success increases with the number of plant species being considered. We expect that when only one plant species is considered, then the importance of community structure will be negligible, while we expect this importance to increase as more plant species are considered (up to a maximum number of 6 species which is the maximum we have measured in our study at a particular site).

@@

At the species level, our results show that in the case of fruitset, both model 1 and model 2 are equally good in explaining the variability observed when accounting for model complexity (i.e.,$\Delta AIC<2$), and therefore we cannot select one over the other. Given that model 2 has a greater number of variables which penalize for the added complexity, we will thus comment results only for model 2, which in the case of fruitset shows a positive effect of the diversity of species visiting a focal plant species (measured using the species´normalised degree, Fig. XX) as well as a positive effect of the centrality of the focal plant on its fruitset.

@@

For all other measures of reproductive success considered (i.e., the number of seeds per fruit, fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only included simple visitation metrics (in this case, the diversity of visiting pollinators and the total number of visits received by a focal plant species). However, none of the variables included within our model explain the differences observed. [show in sup mat?]()

@@

At the network level, we find different patterns for fruitset and the number of seeds per fruit as compared to those for fruit and seed weight. In the case of fruitset and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed (i.e.,$\Delta AIC<2$). Again, because this suggests model 2 is a good model despite its added complexity we will comment results for this model only. In particular, we find that both fruitset and the number of seeds per fruit are positively related to functional complementarity between pollinators. Additionally, we find a negative effect of community-level pollinator species diversity on average fruitset.

@@

When evaluating the effect of differences in community composition and structure for equity in reproductive success across the different individuals within a species and site we find that both model 1 and model 2 are equally good (i.e.,$\Delta AIC<2$) and thus we cannot select one over the other. Specifically, regarding the results for model 2, we find a significant and positive effect of nestedness for equity between individuals of a species (Table X, Fig. X). This effect that we find when using a 50% threshold of productivity (i.e., when looking at plant species that are producing 50% of the maximum fruitset observed for the area), is however not maintained when using 25 and 75% thresholds. In particular, when using a 25% threshold we find model 1 is the best model and none of the variables considered are able to explain the differences observed. Contrastingly in the case of the 75% threshold, we find again that both model 1 and 2 are equally plausible but in this case we find a positive effect of functional complementarity between pollinators for equity in fruitset across individuals within a species.
[this is interesting, as selfing rates I expect to be ~ 40%... In any case I am confused now on this calculation]()

@@

#EQUITY IN INDIVIDUALS WITHIN SPECIES

library(vegan)
library(plyr)

fr.max<-aggregate(.~ Plant.sp, f3, FUN=max)

f3$fruit.max<-fr.max$tot.fruitset[match(f3$Plant.sp, fr.max$Plant.sp)]

f3$fruit.prop<-f3$tot.fruitset/f3$fruit.max
f5<-subset(f3, f3$fruit.prop>0.5)
f5$no_rows<-rep(1, nrow(f5))
head(f5)

#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
f6<- aggregate(no_rows ~ Site_ID + Plant.sp, f5, length)
head(f6)

#because when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can oscar max = 4 we corrected for this doing % above threshold, and no number.

f3$no_rows<-rep(1, nrow(f3))
f3b<- aggregate(no_rows ~ Site_ID + Plant.sp, f3, length)
head(f3b)

f3b$j<- paste(f3b$Site_ID, f3b$Plant.sp)
f6$j<- paste(f6$Site_ID, f6$Plant.sp)

f6$total.plant.numb<-f3b$no_rows[match(f6$j, f3b$j)]
f6$equity<-f6$no_rows/f6$total.plant.numb

@@

f6$nodf.song<-out.site$nodf.song[match(f6$Site_ID, out.site$Site_id)]
f6$functional.comp.poll<-out.site$functional.comp.poll[match(f6$Site_ID, out.site$Site_id)]
f6$species.poll<-out.site$species.poll[match(f6$Site_ID, out.site$Site_id)]
f6$tot.visits<-f.agg$tot.visits[match(f6$Site_ID, f.agg$Site_ID)]

#scale all variables

f6$nodf.song.sc <- scale(f6$nodf.song, center = T, scale = T)
f6$functional.comp.poll.sc <- scale(f6$functional.comp.poll, center = T, scale = T)
f6$species.poll.sc <- scale(f6$species.poll, center = T, scale = T)
f6$tot.visits.sc <- scale(f6$tot.visits, center = T, scale = T)

#fit two models
m1.eq<-glmer(equity ~  species.poll.sc + tot.visits.sc + (1|Site_ID), family="binomial", data=f6)

summary(m1.eq)

vif(m1.eq)

m2.eq<-glmer(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc+ (1|Site_ID), family="binomial", data=f6)
#nich estimate not overlaping zero: 0.6178     0.4354, second higher effect size!
summary(m2.eq)

vif(m2.eq)

@@

AICtab(m1.eq, m2.eq) #Almost equal... Again, for prediction, go with the simple, for mechanistic understanding, look into niche partitioning. 
library(remef)
y_partial_eq <- remef(m2.eq, fix = c("species.poll.sc", "tot.visits.sc", "functional.comp.poll.sc"), ran = "all", inverse = F)
y_partial_eq_inv<-exp(y_partial_eq)/(1+exp(y_partial_eq))

pl.th_ <-ggplot(f6,  aes(x=nodf.song.sc, y=y_partial_eq_inv ))+      
  geom_point(size=4, color="black") + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) +  ylim(0,1.1) +
  xlab("Nestedness") +      
  ylab("Equity in fruitset") + theme_bw() + 
  theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))

#pl.th_ #oh yeah!

#now 75% threshold
#head(f3)
f5.75<-subset(f3, f3$fruit.prop>0.75)
f5.75$no_rows<-rep(1, nrow(f5.75))
head(f5.75)

#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
f6.75<- aggregate(no_rows ~ Site_ID + Plant.sp, f5.75, length)
head(f6.75)

#because when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can oscar max = 4 we corrected for this doing % above threshold, and no number.

f3$no_rows<-rep(1, nrow(f3))
f3b<- aggregate(no_rows ~ Site_ID + Plant.sp, f3, length)
head(f3b)

f3b$j<- paste(f3b$Site_ID, f3b$Plant.sp)
f6.75$j<- paste(f6.75$Site_ID, f6.75$Plant.sp)

f6.75$total.plant.numb<-f3b$no_rows[match(f6.75$j, f3b$j)]
f6.75$equity<-f6.75$no_rows/f6.75$total.plant.numb

@@

##equity in seed number???

>>>>

Title: Interaction network structure maximizes community-level plant reproduction success via niche complementarity

@@

Short running title: Network structure effects on reproductive success

Keywords: nestedness, niche complementary, fruitset, pollination, plant-pollinator interaction

@@

Words in Abstract: 147 words

@@

Declines in pollinator diversity and abundance have been reported across different regions, with implications for the reproductive success of plant species. However, research has focused primarily on pairwise plant-pollinator interactions, largely overlooking community-level dynamics. Yet species do not interact in isolation, they are embedded within larger networks whose structure can affect pollinator functional roles and, ultimately, the pollination services they deliver to plants. Here, we present one of the first efforts linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 well-resolved networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems. We find that, for prediction purposes, information on simple visitation metrics is sufficient. Contrastingly, a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on community structure, particularly that reflecting niche complementarity between pollinators.

@@

Pollinators provide key services to plants by facilitating pollen flow between individuals. The recent declining trends found for some pollinator species in some regions of the planet ([@Potts2010], although see [@I.2019] reflecting general lack of knowledge at the global level), have led many researchers to focus on the functional impacts of these changes in pollinator diversity, with a major focus being placed on the consequences for plant reproductive success [@Biesmeijer2006].

Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012a; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain differences found  across different plant individuals. Some have gone a step further by including information on the efficiency of these visits, thus adding a measure of quality to the pollination services [@Willcox2017]. Contrastingly, community-level analyses remain scarce [@Bennett2018]. Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species. We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect ones between species within one guild (e.g., plants) through their shared resources [@Carvalheiro2014; @Lazaro2014; @Mayfield2017]. Understanding how changes in pollinator diversity and interaction structure affect whole community assemblages is thus a major challenge that requires attention.

The few pollination studies that have analysed the effects of changing pollinator diversity for reproductive success at the community level, have done so using mainly experimental setups. As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found that not only pollinator species diversity had an effect for average reproductive success, but also they found that community structure had an important effect [@Frund2013]. In particular, these authors found that niche complementarity between pollinators, in terms of plant species and temperature coverage (a measure of the overlap in the use of plant resources and optimum temperature activity) had a positive effect for average seed set at the community level [@Frund2013]. This provides added information on the effects of biodiversity for ecosystem functioning, suggesting that not only the diversity of species present but also the diversity of roles and ways in which a community is structured are determinant factors.

Indeed, theoretical research has long suggested that the structure of a community has an effect for ecosystem functioning (reviewed in [@Thompson2012]). This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data (but see [@Poisot2013]). Specifically, a major knowledge gap resides in understading which aspects of structure determine which aspects of function [@Thompson2012]. We are now at a point in which there is considerable understanding on the attributes characterizing mutualistic interaction networks [@Bascompte2007b] and we have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016]. Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures [Bascompte et al 2013 PNAS] or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004]. However, how the structure shaping this network of interactions affects key ecosystem functions such as plant reproduction remains untested [@Winfree2013]. The time is thus ripe to use this knowledge to explore relationships between community structure and ecosystem functioning, with special emphasis being placed on the underlying mechanisms that drive these relationships.

Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level. To this end, we use a well-replicated dataset encompassing 16 well-resolved plant-pollinator interaction networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain. Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success. In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success. In addition, we evaluate whether community structure helps us explain differences in equity in reproductive success across individuals within a species and species within a community as a measure of evenness and [stability in the pollination service??]()

Our results suggest that for prediction purposes, information on simple visitation metrics, particularly regarding the diversity of pollinators that visit a plant species, is sufficient. However, we find that a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success requires additional information on network structure, notably information on the complementarity between the functions performed and the niches occupied by different pollinator species.

[IB: this intro is brilliant!]() THANK YOU!! :) :)

@@

Our study was conducted in SW Spain within the area of influence of Doñana National Park (Figure 1?). Here, we surveyed 16 Mediterranean woodland patches, located within a XXX m2 area and with an average distance of XX km between them (min= XX, max= XX). [SHOULD WE SAY SOMETHING ABOUT THE MATRIX SURROUNDING THESE SITES OR THE TYPE OF VEGETATION PRESENT IN THEM??? IB: I don't think is relevant. ASK CURRO ABOUT THE NUMBERS ABOVE.]() Each site was surveyed 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins. Along each transect, we identified all plant species and recorded all the flower visitors (including bees, hoverflies, beetles and XX) [IS IT JUST BEES AND HOVERFLIES? IB: NO, ALL VISITORS!]() that legitimately visited them. Floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FdPM with the aid of experts in the different taxonomic groups (see acknowledgements). All surveys were done under similar weather conditions, avoiding windy or rainy days.

@@

Within each site, we marked between 2 and 12 individuals (6.49 +- 2.37) of 1 [NB: Which site has only one species!]() [AM: Elpinar only has Rosmarinus and Villamanriqueeste only Cistus salvifolius]() to 6 plant species (4.06 +- 1.69), depending on the availability and presence of flowers during the sampling events. For each individual, we counted the number of flowers at each sampling point and recorded fruitset, the number of seeds per fruit (for 2-36 fruits, 11.17 +- 6.84) and average seed weight per fruit at the end of the season. Our survey included a total of 19 different plant species across our 16 sites.

@@

In order to analyse how differences within the community structure might affect plant reproductive success, we constructed weighted plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling. We thus obtained one weighted interaction network per site, representing the frequency of visits by different pollinator species to different plant species. For each network, we then proceeded to extract a series of relevant network metrics.

@@

At the community level, we followed the same logic as the one presented at the species level. Thus, we also calculated two network metrics providing complementary non-redundant information. In this case we focused on (i) nestedness and (ii) niche complementarity. Nestedness is the property by which specialists interact with a subset of the species that generalists interact with [@Bascompte2003]. Although there is an ongoing debate in the literature, some studies have found that nested networks are more stable and resilient to perturbations because nestedness promotes a greater diversity by minimizing competition among species in a community [@Bastolla2009]. However, many network attributes vary with network size and complexity [@Bluthgen2006]. In the case of nestedness, we know it can be affected by network size and connectance [@Song2017]. An approach that is often used to correct for this, is to use null models and to compare null-model corrected nestedness values across different networks. However, this approach has been recently shown to present the same issues, as z-scores also change with network size and connectance [@Song2017]. We thus followed the advice provided by Song et al. (2017) by using a normalized value of the widely-used nestedness metric NODF [@Almeida-Neto2011], $NODF_c$. This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance, S is network size and $NODF_n = NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017].

Nevertheless, plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]). Yet at present we do not know how the interplay between redundancy and complementarity in species roles determines reproductive success. To calculate niche complmentarity we used a community-level measure defined as the total branch length of a functional dendrogram based on qualitative differences in visitor assemblages between plants [@Devoto2012; @Petchey2007a]. All network metrics were calculated using package bipartite [@Dormann2009].

@@

At the species level, model 1 included as explanatory variables the diversity of pollinator species visiting a focal plant and the total number of visits received by that plant species; while model 2, added the two network attributes calculated at the species level: average niche overlap and centrality. In this case, we included plant species nested within site as a random effect to account for the non-independence of several individuals measured for the same plant species within each site. The diversity of pollinator species visiting a focal plant was approximated using the plant´s normalised degree, i.e., the number of links with different pollinator species a plant has, scaled by the number of possible partners [@Dormann2009]. Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the morisita index  (@Manual{,
    title = {spaa: SPecies Association Analysis},
    author = {Jinlong Zhang},
    year = {2016},
    note = {R package version 0.2.2},
    url = {https://CRAN.R-project.org/package=spaa},
  }). As a measure of centrality we used weighted closeness centrality which describes centrality through the path lengths of a species to other species in the network using a weighted representation of the network [@Dormann2009]. Response variables included fruitset for different individuals measured per species analyzed using a binomial distribution, the number of seeds per species for different individuals analyzed using normal distribution and average values per species of fruit and seed weight fitted to poisson distributions.

At the community level, we upscaled our species-level analyses. In this case, model 1 included total pollinator diversity and the total number of visits received by all plants within the community as explanatory variables. Model 2, in turn, added information on community structure by including nestedness and niche complementarity as explanatory variables. As response variable we had the average reproductive success for the whole community (i.e., average fruitset analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight previously scaled for each species for which we used normal distributions). We thus had a single value per site and no random effects are needed in this case.

Average values of reproductive success at the community level can be driven to a large extent by a single plant species. Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” or evenness in reproductive success across the whole community. We therefore calculated a measure of equity in reproductive success at the community level as the proportion of species within a community with normalized average fruitset values above 0.5. We repeated this using 0.25 and 0.75 thresholds. We then used the same framework as before and fit the same models 1 and 2 GLMs as the ones used at the community level, but using equity in reproductive success as the response variable and a binomial distribution. In this case, we retained only sites for which we had at least measured reproductive success for 2 plant species (N=14 sites). 
We used information criterion methods to find the best model for each case and selected the ones with the lowest Akaike Information Criterion (AIC) value. $\Delta AIC<2$, were not considered enough to select one model over the other [@Burnham2011].

@@

Finally, we tested whether the importance of community structure in explaining differences in equity in reproductive success within communities increases with the number of plant species being considered. We expect that when only one plant species is considered, then the importance of community structure will be negligible, while we expect this importance to increase as more plant species are considered (up to a maximum number of 6 species which is the maximum we have measured in our study at a particular site).

@@

At the species level, in the case of fruitset, our results show that both model 1 and model 2 are equally good in explaining the variability observed (i.e.,$\Delta AIC<2$), and therefore we cannot select one over the other. Given that model 2 has a greater number of variables which should be penalized given the added complexity it provides, we will comment results only for model 2. In this case, we find a positive effect of pollinator species diversity (measured using the species´normalised degree, Fig. XX) as well as a positive effect of the centrality of the focal plant on its fruitset.

@@

For all other measures of reproductive success considered (i.e., the number of seeds per fruit, fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only included simple visitation metrics (in this case, pollinator species diversity and the total number of visits received by a focal plant species). However, none of the variables included within our model explain the differences observed. [show in sup mat?]()

@@

At the network level, we find different patterns for fruitset and the number of seeds per fruit as compared to those for fruit and seed weight. In the case of fruitset and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed (i.e.,$\Delta AIC<2$). Again, because this suggests model 2 is a good model despite its added complexity, we will comment results for this model only. In particular, we find that both fruitset and the number of seeds per fruit are positively related to niche complementarity between pollinators. Additionally, we find a negative effect of community-level pollinator species diversity on average fruitset.

@@

When evaluating the effect of differences in community composition and structure for equity in reproductive success across the different species within a community we find that model 1 is the best model for all the thresholds considered (50%, 25% and 75%). However, we find that none of the variables considered are able to explain the differences observed. 
[this is interesting, as selfing rates I expect to be ~ 40%... In any case I am confused now on this calculation]()

@@

#normalize fruitset values for individuals within species and sites, to have values between 0 and 1

range01 <- function(x){(x-min(x))/(max(x)-min(x))}
f2_scaled_fruit <- f2 %>% group_by(Plant.sp) %>% mutate(tot.fruitset = range01(tot.fruitset))

#calculate average normalized fruitset values per site to have one unique value per site
f.ag.pr <- ddply(f2_scaled_fruit, c("Site_ID", "Plant.sp", "nodf.song", "functional.comp.poll", "species.poll"), 
              summarise, tot.visits    = sum(tot.visits),
              mean.fruitset = mean(tot.fruitset))

#select species with normalized values >0.5
f.ag_scaledb<-subset(f.ag.pr, f.ag.pr$mean.fruitset>0.50)

#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
f.ag_scaledb$no_rows<-rep(1, nrow(f.ag_scaledb))
f4c<- aggregate(no_rows ~ Site_ID, f.ag_scaledb, length)
head(f4c)

#because when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can score max = 4 we corrected for this doing % above threshold, and no number. 
#calculate total number of species per site
f4$no_rows<-rep(1, nrow(f4))
f4d<- aggregate(no_rows ~ Site_ID, f4, length)
head(f4d)

f4c$total.plant.numb<-f4d$no_rows[match(f4c$Site_ID, f4d$Site_ID)]

#remove sites that only have one plant sps, Elpinar and Villamanriqueeste
f4e<-subset(f4c, f4c$total.plant.numb>1)

#calculate equity as proportion of species with >50% of fruitset compared to total number of sps
f4e$equity<-f4e$no_rows/f4e$total.plant.numb

@@

f4e$nodf.song<-out.site$nodf.song[match(f4e$Site_ID, out.site$Site_id)]
f4e$functional.comp.poll<-out.site$functional.comp.poll[match(f4e$Site_ID, out.site$Site_id)]
f4e$species.poll<-out.site$species.poll[match(f4e$Site_ID, out.site$Site_id)]
f4e$tot.visits<-f.agg$tot.visits[match(f4e$Site_ID, f.agg$Site_ID)]

f4e$species.pl<-out.site$species.pl[match(f4e$Site_ID, out.site$Site_id)]
#scale all variables

f4e$nodf.song.sc <- scale(f4e$nodf.song, center = T, scale = T)
f4e$functional.comp.poll.sc <- scale(f4e$functional.comp.poll, center = T, scale = T)
f4e$species.poll.sc <- scale(f4e$species.poll, center = T, scale = T)
f4e$tot.visits.sc <- scale(f4e$tot.visits, center = T, scale = T)
f4e$species.pl.sc <- scale(f4e$species.pl, center = T, scale = T)

#fit two models
 m1.eq.comm<-glm(equity ~  species.poll.sc + tot.visits.sc , family="binomial", data=f4e)

 m2.eq.comm<-glm(equity ~  species.poll.sc + tot.visits.sc + nodf.song.sc + functional.comp.poll.sc , family="binomial", data=f4e)
summary(m2.eq.comm)

@@

AICtab(m1.eq.comm, m2.eq.comm) #m1 is best no variables significant

#save table with results for paper, both models are equally good so save both tables
summ.eq<-round(summary(m1.eq.comm)$coef, digits=2)
#write.csv(summ.eq, file="tables/resultsequityNETWORKm1.csv", row.names = TRUE)

#test for problems in residuals
# res<-simulateResiduals(m1.eq.comm)
# plot(res, rank = TRUE)

f75<-subset(f.ag.pr, f.ag.pr$mean.fruitset>0.75)

#for each site here is the number of sps whose fruitset exceeds 75% of maximum fruitset observed in the whole study area
f75$no_rows<-rep(1, nrow(f75))
f75b<- aggregate(no_rows ~ Site_ID, f75, length)
head(f75b)

#because when calculating thresholds, sites with 6 plants can score up to 6, but sites with 4 sites can score max = 4 we corrected for this doing % above threshold, and no number. 
#calculate total number of species per site
f4$no_rows<-rep(1, nrow(f4))
f4d<- aggregate(no_rows ~ Site_ID, f4, length)
head(f4d)

f75b$total.plant.numb<-f4d$no_rows[match(f75b$Site_ID, f4d$Site_ID)]

#remove sites that only have one plant sps, Elpinar and Villamanriqueeste
f75c<-subset(f75b, f75b$total.plant.numb>1)

#calculate equity as proportion of species with >50% of fruitset compared to total number of sps
f75c$equity<-f75c$no_rows/f75c$total.plant.numb

@@
